Open source landscape ecology tools \thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2020-10-15 paper/paper.Rmd
cleans text

To better understand how *R* is used by the landscape ecology community, we designed a short survey and used mailing lists and social media to reach the landscape ecology community. 
In total, the survey was answered by `r n_people` participants, of which the the majority were either "PhD students" (`r current_position[[1, 2]]`%), followed by "Post-Docs" (`r current_position[[2, 2]]`%) and "Professors" (`r current_position[[3, 2]]`%). Other less frequent answers were "data scientists", "government employees" or "bachelor's and master's degree students". 
Most people used R either "daily" (`r usage_freq[[1, 2]]`%) or a "few times a week" (`r usage_freq[[2, 2]]`%) and and about half of all participants described themselves as "advanced" user (`r expertise[[1, 2]]`%), while still `r expertise[[2, 2]]`% described themselves as "intermediate" users. 
Related to this, about half of the participants either implemented their own package (`r own_package[[3, 2]]`%), or plan to do so in the future (`r own_package[[2, 2]]`%) and most of these packages are hosted on *GitHub* and/or *CRAN*.

@@

Interestingly, most people use the raster data model (`r data_model[[1, 2]]`%) in comparison to the vector data model (`r data_model[[2, 2]]`%). 
This was also represented in the most used *R* packages (Fig. \@ref(fig:fig-packages-tasks) A))
When asked for the three most used packages, participants of the survey listed `r length(unique(r_packages))` packages in total. The *raster* packages was listed the most, followed by the *sf* package. 
Because both the *raster* and the *sf* are designed for basic and advanced data handling and processing of raster and vector data, respectively, it is not surprising that "(pre-)processing of spatial data" was the most important workflow task for the majority of the survey participants (Fig. \@ref(fig:fig-packages-tasks) B)).

>>>>

To better understand how *R* is used by the landscape ecology community, we designed a short survey and used mailing lists and social media to reach the landscape ecology community. 
In total, the survey was answered by `r n_people` participants, of which the the majority were either "PhD students" (`r current_position[[1, 2]]`%), followed by "Post-Docs" (`r current_position[[2, 2]]`%) and "Professors" (`r current_position[[3, 2]]`%). Other, less frequent answers, were "data scientists", "government employees" or "bachelor's and master's degree students". 
Most people used R either "daily" (`r usage_freq[[1, 2]]`%) or a "few times a week" (`r usage_freq[[2, 2]]`%) and about half of all participants described themselves as "advanced" user (`r expertise[[1, 2]]`%), while `r expertise[[2, 2]]`% described themselves as "intermediate" users. 
Related to this, about half of the participants either implemented their own package (`r own_package[[3, 2]]`%) or plan to do so in the future (`r own_package[[2, 2]]`%) and most of these packages are hosted on *GitHub* and/or *CRAN*.

@@

Interestingly, most people use the raster data model (`r data_model[[1, 2]]`%) in comparison to the vector data model (`r data_model[[2, 2]]`%). 
This was also represented in the most used *R* packages (Fig. \@ref(fig:fig-packages-tasks) A).
When asked for the three most used packages, participants of the survey listed `r length(unique(r_packages))` packages in total.
The *raster* package was mentioned the most, followed by the *sf* package. 
Because both the *raster* and the *sf* are designed for basic and advanced data handling and processing of raster and vector data, respectively, it is not surprising that "(pre-)processing of spatial data" was the most important workflow task for the majority of the survey participants (Fig. \@ref(fig:fig-packages-tasks) B).

### 2020-10-15 paper/paper.tex
improves plots
cleans text

To better understand how \emph{R} is used by the landscape ecology community, we designed a short survey and used mailing lists and social media to reach the landscape ecology community.
In total, the survey was answered by 94 participants, of which the the majority were either ``PhD students'' (33\%), followed by ``Post-Docs'' (26.6\%) and ``Professors'' (12.8\%). Other less frequent answers were ``data scientists'', ``government employees'' or ``bachelor's and master's degree students''.
Most people used R either ``daily'' (58.5\%) or a ``few times a week'' (34\%) and and about half of all participants described themselves as ``advanced'' user (48.9\%), while still 39.4\% described themselves as ``intermediate'' users.
Related to this, about half of the participants either implemented their own package (20.2\%), or plan to do so in the future (22.3\%) and most of these packages are hosted on \emph{GitHub} and/or \emph{CRAN}.

Interestingly, most people use the raster data model (70.2\%) in comparison to the vector data model (29.8\%).
This was also represented in the most used \emph{R} packages (Fig. \ref{fig:fig-packages-tasks} A))
When asked for the three most used packages, participants of the survey listed 75 packages in total. The \emph{raster} packages was listed the most, followed by the \emph{sf} package.
Because both the \emph{raster} and the \emph{sf} are designed for basic and advanced data handling and processing of raster and vector data, respectively, it is not surprising that ``(pre-)processing of spatial data'' was the most important workflow task for the majority of the survey participants (Fig. \ref{fig:fig-packages-tasks} B)).

@@

\caption{Evaluation of the usefullnes o fR for landscape ecology by the particpants of the survey. Answers were possible on a 5-point scale.}\label{fig:fig-usefulness}
\end{figure}

>>>>

To better understand how \emph{R} is used by the landscape ecology community, we designed a short survey and used mailing lists and social media to reach the landscape ecology community.
In total, the survey was answered by 94 participants, of which the the majority were either ``PhD students'' (33\%), followed by ``Post-Docs'' (26.6\%) and ``Professors'' (12.8\%). Other, less frequent answers, were ``data scientists'', ``government employees'' or ``bachelor's and master's degree students''.
Most people used R either ``daily'' (58.5\%) or a ``few times a week'' (34\%) and about half of all participants described themselves as ``advanced'' user (48.9\%), while 39.4\% described themselves as ``intermediate'' users.
Related to this, about half of the participants either implemented their own package (20.2\%) or plan to do so in the future (22.3\%) and most of these packages are hosted on \emph{GitHub} and/or \emph{CRAN}.

Interestingly, most people use the raster data model (70.2\%) in comparison to the vector data model (29.8\%).
This was also represented in the most used \emph{R} packages (Fig. \ref{fig:fig-packages-tasks} A).
When asked for the three most used packages, participants of the survey listed 75 packages in total.
The \emph{raster} package was mentioned the most, followed by the \emph{sf} package.
Because both the \emph{raster} and the \emph{sf} are designed for basic and advanced data handling and processing of raster and vector data, respectively, it is not surprising that ``(pre-)processing of spatial data'' was the most important workflow task for the majority of the survey participants (Fig. \ref{fig:fig-packages-tasks} B).

@@

\caption{Evaluation of the usefullnes of R for landscape ecology by the particpants of the survey. Answers were possible on a 5-point scale.}\label{fig:fig-usefulness}
\end{figure}
